Adopting agile in the large: motivations, success factors and challenges

### 2014-05-10 journal/article.tex
Work in progress

% Using two models side by side

@@

@@

@@

[P17] Like many organizations, BMC’s decision to adopt Agile practices started
in the development organization.

@@

* General problem: Development had to comply with incompatible surrounding
* Not agile: Production activities
[P1]
Comment: This group is the development group. Most of the elements of this
group’s TF led to a definition and practice of their development methods very
close to the agile manifesto. However, they have used this to differentiate
themselves from the rest of the organisation and have employed  workarounds in
order to comply with an incompatible sociotechnical network.  Although the
organization has become more tolerant of agile practices most of the existing
production activities remain difficult to integrate with Agile.

* General problem: There was not agreement to introduce agile to all levels and functions in the organization
* Tension was created in the organization
[P1]
Three of the groups saw Agile as having value for them, while ‘the business’
apparently do not see the value of Agile at all. One of the challenges faced by
this organization is how to extend an agile way of thinking beyond the
developers, and both the Agile Advocates and Project Z believed that agile
should cover the entire process, while the development team were content with
focusing on implementation only. This shows a tension in the process of
sociotechnical change: trying to translate principles created for the
development of software into broader knowledge and processes to an audience with
different roles, understandings and expectations, sharing a contrasting TF. One
thing (the only thing) which all groups agreed upon was that increased
collaboration would result in a better product.

* General challenge: moving agile from development to the rest of business
[P2]
A group of Agile Advocates and Coaches is driving the agile ‘push’. Their
mission is to disseminate knowledge of agile methods and facilitate their
successful adoption across the organisation. From a TF perspective, this means
that advocates must persuade other staff to adopt the same elements of
interpretation and practice to frame agile adoption as their own. One of the
biggest challenges they were facing was to move Agile from the development teams
into the rest of the business.

* Problem: Collaboration is needed between all stakeholders --> Stakeholders do not share viewpoints which creates conflicts in interests
* All communities should engage in the process earlier
[P2]
Another element of interpretation was the need for greater collaboration and
communication across all stakeholders and the  problems associated with it,
especially between marketing managers and IT delivery managers. The IT delivery
manager characterized the differences by saying: “I (marketing says) want that
box and I want that now, whereas we (IT delivery) unpack the box”. The technical
architect agreed that all communities need to engage earlier in the process so
that decisions make sense from a customer, business and technical point of view.

* Development was content with using agile only internally
* General problem: Scaling agile practices into use in different roles
[P2]
One of the challenges faced by this organisation is how to extend an agile way
of thinking beyond the developers, and both the Agile Advocates and Project Z
believed that agile should cover the entire process, while the development team
were content with focusing on implementation only. This shows a tension in the
process of sociotechnical change: trying to translate principles created for the
development of software into broader knowledge and processes to an audience with
different roles, understandings and expectations, sharing a contrasting TF.

* Not agile: MRDs --> Stories had to be extracted from detailed documentation --> Not good
* MRDs not based on reality
[P2]
Extracting user stories from existing, very detailed ‘marketing requirements
documents’ (MRDs) was another workaround. These MRDs were a prominent artifact
found across the organisation. Leaders of Project Z claimed that it was very
difficult to work with such detailed documents in a project whose scope could
change rapidly; one agile developer described MRDs as “not based in reality at
all”.

Comment:
The problem with MRDs is a symptom of the challenge to integrate "the business" with the agile process.

* Problem: PMO is employing a waterfall paradigm
[P3]
the Amazon PMO may some day become interested in Scrum, but they are enmeshed in
maintaining and thriving within a traditional waterfall paradigm. Another
example is the existence of separate QA groups. Executive sponsorship would help
to begin to break down these entrenched impediments.

* Problem: There was a gap between marketing or product management and development --> Requirement elaboration as cause
[P5]
We were able to successfully bridge the gap between marketing or product
management feature and the detailed requirements that are required for Agile.

* Problem: Management attempts to use a ``resource pool'' of individuals rather than coordinating teams
[P6]
we face the constant threat that restructuring and the instinct from management
to track and leverage resources at the individual level (for example
organization-wide resource pools) will destroy the team dynamic and adversely
affect productivity.

* Challenge: PMO with entrenched processes
* Challenge: Process group at odds with Scrum teams
[P6]
Align with Project Management: In any large organization like Yahoo! there
inevitably exist Project Management Offices with entrenched process control
practices. We had conflicts arise in our international offices as they had
continued to roll out the original PDP during the U.S. transition to Scrum. The
teams attempting to use Scrum were often at odds with the process group and, as
a result, the two groups were not communicating well. We tackled this challenge
by building relationships and identifying the common goals that both groups were
focused on achieving.

@@

While moving to agile was clearly a success for the R&D organization at
salesforce.com, the initial transition period was far from smooth for the User
Experience team.  In 2006, the vast majority of literature on the topic of agile
did not include guidance on the inclusion of User-Centered Design (UCD)
processes [4].  In agile literature, ‘design’ typically referred only to coding
or system design [1].  The User Experience team was left with many unanswered
questions; some included:
• How can we properly identify the target users and ensure that their needs are
met within agile’s just-in-time process?
• How can we accomplish holistic design when agile teams are planning and
building features in a piecemeal fashion?
• How do UX professionals succeed across multiple teams when agile espouses one
team per person?
The unhappiness of the UX team was illustrated clearly in the results of a
survey sent out to the R&D organization about 6 months after the rollout. 
Eighty percent of total respondents felt that agile was making their Scrum team
more effective. However, when looking at the data by functional area, only 30\%
of User Experience team members agreed with this statement.  When asked about
several other impacts of agile, the same trend was seen (Figure 3).

@@

* Problem: User Experience design was a long process --> Timeboxing to sprints compromised quality of design
[P15]
Tighter timelines were also mentioned. In Scrum, teams select what they will
work on at the beginning of a sprint and then build those items to completion
over the course of that sprint; in the case of salesforce.com that is a one
month period of time, start to finish. These aggressive timeframes can cause UCD
to be compromised, since investigating and iterating designs often takes longer
than weeks, particularly for complex enterprise applications.  In this initial
phase, the User Experience team struggled to find ways to achieve the success
that they had reached using waterfall. The R&D division made significant
progress using agile, though, so the UX team had no choice but to adapt and
evolve.

@@

* General challenge: Agile practices work worse in non-development
[P18]
Agile practices worked well in development teams and some other teams. Not
surprisingly, the more distant from development, the less successful the pilot.

“Why change? Agile practices will not suit us.” The further away from actual
software development, the less understanding about what benefits Agile ways of
working will bring. The idea that Agile works best if customer contact and
customer contract are synergistic does not easily penetrate a large
organization.

* New development moved to agile first 
* Problem: Moving the product from early access to GA --> Value chain has traditional parts
[P31]
The biggest bricks in our Two-Year Wall were being laid outside the development
organization. The basic principles of Agile and lean are to reduce waste and
deliver working software to the customer as often as possible. However, the
development organization does not do this alone. When you look at the end-to-end
process, there are many other functions involved:  sales, marketing, legal,
finance. What we didn’t understand when we first embarked upon the Agile journey
is what a disruptive force our approach would be on the entire company. As I
mentioned earlier, the first teams to transition to Agile were those working on
a new set of products. These teams had been working very closely with a
strategic customer, and in the months prior to the public release of these
products the situation was ideal for the collaboration, iteration and pace of
releases. The reality is, in the first 18 months of our transformation the
original Agile teams were operating as an “Agile microcosm” insulated from the
rest of our traditional, multi-phased business processes. Once it became time to
move the product from “early access” to general availability – to move from
factory to inventory – things started to come apart.  Friction arose as the
Agile teams began bumping up against the other, traditional, parts of the value
chain.

* Problem: Teams completed backlog --> Continued with stories direct from customer --> Signe customer bias
* Problem: Sales and marketing organization had a different vision of the product
* Problem: Product marketing was not collaborative, and in old mindset
* Problem: Requirements --> user stories more granular and prioritized
[P31]
After several months of working on the new products, the Agile teams “drained”
the backlog.   For a while, they kept busy working on new user stories that came
directly from the strategic customer.  This began to lead to a disconnect
between what the marketing and sales organizations believed to be the overall
direction of the product, and the actual direction it was taking based on the
needs of a single customer. It was clearly time for a regroup, and the
engineering team pushed back on the MRD.  They were in full production mode
using Agile and they needed more granular, prioritized user stories to fuel
their efforts.  The teams needed product marketing to be more collaborative in
the decomposition of the requirements. This was a totally foreign concept for
the product marketing team. They had approached the relationship with
engineering as a “black box” – high level requirements went in, and something
eventually came out (usually late, and sometimes off the mark on what they
expected).

@@

* Solution: Development and product marketing work together
* Solution: Product marketing can require a release to be completed in 90 days
[P31] Maples 2009 - Enterprise Agile Transformation - The Two-Year Wall.pdf - 31:18 [What we instituted was what we..]  (5:1983-5:2374)   (Super)
Codes:  [C: Adapting non-development parts of organization to agile - Family: RQ3: Challenges] 
No memos
What we instituted was what we call an “Iron Triangle.” The concept is that at
some number of sprints out before a release, we would commit to delivering a
fixed set of features and functionality  at a certain date.  Of course, there
was always the opportunity for us to deliver more than what we committed to, 
but we absolutely had to deliver the set features by the set date.

@@

* Development adopted first --> No plans for how to further adopt the rest of the stakeholders
* Challenges: Product stakeholders and management, marketing, and rest of business
* Problem: Marketing --> Lead time for marketing material
* Solution: non-development groups learned how to work more efficiently
[P38]
Another challenge was teaching the rest of the business how to interact,
participate, and collaborate. This is not limited to the product stakeholders
and management but also HR, facilities, IT, and marketing. Marketing has
interesting and important requirements. There are lead times for printing
material such as fliers, brochures, and conference booth banners. Press releases
need to have design down to best show off the product’s content. When suddenly
the site that is the product in many of these cases could change literally on a
week to week basis, you can see some of the issues that had to be addressed.
In the agile world people often think “we can figure out how to interface with
the rest of the business once we’ve gotten the team up and running” and while
there are certainly teams that learn to interface with a non-agile business it
is a risk and a barrier to change. In our case we were lucky that with the
support of the CTO we were able to influence many elements of the business to be
more agile themselves, which allowed them to work more effectively with the new
agile development group.

* Challenge: The entire organization must work in the same mode
* Problem: Marketing
[P42]
In order to achieve real flow, the whole organization must work in the same Lean
mode. For example, managing the product as a whole is difficult if the culture
of  neighbouring areas such as Human Resources or Marketing is not aligned with
Lean thinking. Transformation is expanding and the whole organization  is moving
in the same direction.  A seamless organization is needed to  obtain end-toend
benefits.

* Challenge: Product teams need to communicate with business management
* Challenge: Communicating with marketing
* Challenge: Field services
* The ways of working had to be changed for these groups
[P45]
Upscaling methods were mainly driven by theoretical considerations. Implementing
them revealed that the skills and knowledge ofproduct managers and software
architects were often not sufficient to manage a number of Scrum teams
concurrently. Product teams had to communicate with business management,
marketing, and field services who were not fully prepared for how Scrum and the
product teams’ expectations would change their daily work. The process of
software requirements engineering were found to require a major adjustment.

* Challenge: PMO was a bottleneck inhibiting agility
[P46]
To make this journey a success, it was clear that the transformation had to
start with our strong PMO. Here we had the hub of all things project related –
coordination, reporting, process quality assurance, compliance, code performance
quality assurance and the 100+ project managers themselves – in a central place.
Nothing happened without the PMO’s intimate involvement. It was a bottleneck
that just could not exist for the organization to be agile. First and foremost,
all the project managers were returned to their positions in the development
organization, reporting directly to development managers. There the project
managers (PMs) became accountable for project success – no longer were they
simply facilitators and enforcers of the process. While they had always been
accountable for truth in reporting, now they were accountable for results –
their bonus was on the line.

* Problem: Technology operations --> Problems keeping up with development
[P46]
With the inception of agile development, it became apparent that Technology
Operations was not able to keep pace with rapid deployment and dedicated
development teams.  Senior leaders from both development and operations came
together to openly share their thoughts and provide feedback. As an outcome of
those meetings, the Infrastructure Solutions Management team was formed within
the Technology Operations group.  The goal of the team is to provide
infrastructure support for the rapid deployment of applications from inception
to production. Teams are aligned to each development group, with the purpose of
helping the highest priority projects within the group to ensure that the
Technology Operations teams are not being an impediment to development. In
addition, this group will partner with other Technology Operations groups to
streamline processes and enhance the current service catalog or request for
services.

* Challenge: Surrounding organization, internal customers --> manufacturing, customer services, marketing, sales, field and partner enablement, training, demos, documentation, finance
* Problem: They were not familiar with incremental planning --> Before they committed once
[P48]
We have found, though, that the most difficult part of our transition is getting
everything else that must feed and support the product development teams in
place. In the past, supporting and surrounding organizations counted on having a
content commitment once. From this, plans were formed and timelines aligned.
Incremental planning and commitment was something new for the critical internal
customer teams  as well (manufacturing, customer services, marketing, sales,
field and partner enablement, training, demos, documentation, finance, and
senior leaders.)

* Problem: Infrastructure and Operations Teams --> Need to adopt to rapid delivery
[P50]
With the bulk of Engineering forming into Scrum teams and becoming highly
productive, the Infrastructure and Operations Teams remained operating as usual
but continued to fall further behind as there was not enough time to focus on
improving process efficiency.  A significant portion of activity was spent on
short-term low-gain fire-fighting which  only reduced the resources required to
maintain and significantly improve the infrastructure.

@@

>>>>

% Using two models side by side
% Part of the organization is in old mindset

@@

% --> ``Part is in the old mindset''
% * Problem: Management attempts to use a ``resource pool'' of individuals rather than coordinating teams
% [P6]
% we face the constant threat that restructuring and the instinct from management
% to track and leverage resources at the individual level (for example
% organization-wide resource pools) will destroy the team dynamic and adversely
% affect productivity.

@@

Agile methods are typically understood through a set of activities closely
related to software development. Cases describe how development teams were
typically the first entities in the organization that were considered when
introducing agile [P2, P17, P31, P38]. However, development operates in a larger
context, and will need to interface with other organizational functions.
Challenges were faced when exposing other parts of the organization to the agile
mode, and functions that were further away from development were resistant to
change [P2, P18, P31]. A tension was growing between development and broader
roles in the organization [P1]. The full beenfits of the transformation would
not be attained unless the entire organization was set to work along the same
paradigm [P18, P42].

Primary sources listed various functions beyond development that are involved in
bringing products to the market. Marketing was a particularly frequently
mentioned group [P5, P17, P28, P31, P38, P45, P48]. Other groups involved in the
whole of product delivery were sales [P17, P31], infrastructure and operations
[P10, P45, P46, P50], user experience and design [P9, P10, P28], documentation
[P28], legal [P10], security [P10], customer services [P48], and finance [P48].
All of these groups were reported to be affected on some level by the agile
transformation.
% separate QA [P3], --> Later human resources --> Later

Agile affects timings in the software delivery lifecycle which caused two types
of problems. Firstly, the iterativeness of agile models was problematic when
interfacing with other functions. Iterativeness changed the pace of delivery
[P17], and forced design to focus on a shorter scope [P15]. Various groups
feeding and supporting development had earlier committed once to a long term
plan, but in the new arrangement they needed to adjust to incremental delivery
[P48].

Federoff and Courage [P15] describe how the user experience team struggled with
the

--> Iterativeness and UED

--> DS + UED [P6, P9, P10, P15+P28]

The second type of problems was that some release activities would inevitably
have a long lead time, such as acquiring export clearances and licensing
authority. A particular function that required extended periods of stability was
sales and marketing, as they were required to make customer commitments and
communicate upcomming releases a relatively long time ahead. [P31]
[P38] --> See marketing lead time?

The increased delivery speed of development teams caused infrastructure and
operations teams to fall behind, and they were forced to update their way of
working [P46, P50].

Some cases reported that development efforts were controlled on a top level by a
project management office (PMO). The PMO was described as entrenched in a
waterfall paradigm, and the top-level rigidity was causing friction in the
agile adoption [P3, P6]. The PMO was seen as a hub and bottleneck controlling
all aspects of projects, and its central structure had to be dismantled for
the organization to become agile [P46].

Problems in adopting agile were even showing in functions outside the software
delivery lifecycle. A support function that was particularly mentioned to
have issues in agile adoption was human resouces (HR).

@@

UED

@@

SOME KIND OF GENERAL ADJUSTMENT?

* Challenge: Product teams need to communicate with business management
* Challenge: Communicating with marketing
* Challenge: Field services
* The ways of working had to be changed for these groups
[P45]
Upscaling methods were mainly driven by theoretical considerations. Implementing
them revealed that the skills and knowledge of product managers and software
architects were often not sufficient to manage a number of Scrum teams
concurrently. Product teams had to communicate with business management,
marketing, and field services who were not fully prepared for how Scrum and the
product teams’ expectations would change their daily work. The process of
software requirements engineering were found to require a major adjustment.

ITERATIVENESS / SPEEDED UP INCREMENTAL DELIVERY

* Challenge: Surrounding organization adaption
* Internal customers --> manufacturing, customer services, marketing, sales, field and partner enablement, training, demos, documentation, finance
* Problem: They were not familiar with incremental planning --> Originally they committed once
[P48]
We have found, though, that the most difficult part of our transition is getting
everything else that must feed and support the product development teams in
place. In the past, supporting and surrounding organizations counted on having a
content commitment once. From this, plans were formed and timelines aligned.
Incremental planning and commitment was something new for the critical internal
customer teams  as well (manufacturing, customer services, marketing, sales,
field and partner enablement, training, demos, documentation, finance, and
senior leaders.)

LEAD TIME CONSIDERATION

* Marketing causes trouble
* Development adopted first --> No plans for how to further adopt the rest of the stakeholders
* Challenges: Product stakeholders and management, marketing, and rest of business
* Problem: Marketing --> Lead time for marketing material
* Solution: non-development groups learned how to work more efficiently
[P38]
Another challenge was teaching the rest of the business how to interact,
participate, and collaborate. This is not limited to the product stakeholders
and management but also HR, facilities, IT, and marketing. Marketing has
interesting and important requirements. There are lead times for printing
material such as fliers, brochures, and conference booth banners. Press releases
need to have design down to best show off the product’s content. When suddenly
the site that is the product in many of these cases could change literally on a
week to week basis, you can see some of the issues that had to be addressed.
In the agile world people often think “we can figure out how to interface with
the rest of the business once we’ve gotten the team up and running” and while
there are certainly teams that learn to interface with a non-agile business it
is a risk and a barrier to change. In our case we were lucky that with the
support of the CTO we were able to influence many elements of the business to be
more agile themselves, which allowed them to work more effectively with the new
agile development group.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
DEVELOPMENT SUPPORT TEAMS were not satisfied with agile
* UX lacked big picture --> Iterations
* Problem: UX work in a large application is too large to fit in one sprint

@@

While moving to agile was clearly a success for the R\&D organization at
salesforce.com, the initial transition period was far from smooth for the User
Experience team.  In 2006, the vast majority of literature on the topic of agile
did not include guidance on the inclusion of User-Centered Design (UCD)
processes [4].  In agile literature, ‘design’ typically referred only to coding
or system design [1].  The User Experience team was left with many unanswered
questions; some included:
• How can we properly identify the target users and ensure that their needs are
met within agile’s just-in-time process?
• How can we accomplish holistic design when agile teams are planning and
building features in a piecemeal fashion?
• How do UX professionals succeed across multiple teams when agile espouses one
team per person?
The unhappiness of the UX team was illustrated clearly in the results of a
survey sent out to the R\&D organization about 6 months after the rollout. 
Eighty percent of total respondents felt that agile was making their Scrum team
more effective. However, when looking at the data by functional area, only 30\%
of User Experience team members agreed with this statement.  When asked about
several other impacts of agile, the same trend was seen (Figure 3).

@@

* Problem: User Experience design was a long process --> Timeboxing to sprints compromised quality of design
[P15]
Tighter timelines were also mentioned. In Scrum, teams select what they will
work on at the beginning of a sprint and then build those items to completion
over the course of that sprint; in the case of salesforce.com that is a one
month period of time, start to finish. These aggressive timeframes can cause UCD
to be compromised, since investigating and iterating designs often takes longer
than weeks, particularly for complex enterprise applications.  In this initial
phase, the User Experience team struggled to find ways to achieve the success
that they had reached using waterfall. The R\&D division made significant
progress using agile, though, so the UX team had no choice but to adapt and
evolve.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
MARKETING NEEDS TO KNOW ON BEFOREHAND WHAT WILL BE RELEASED

* Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
* Problem: Sales and marketing organization had a different vision of the product
* Problem: Product marketing was not collaborative, and in old mindset
* Problem: Requirements --> user stories more granular and prioritized
[P31]
After several months of working on the new products, the Agile teams “drained”
the backlog.   For a while, they kept busy working on new user stories that came
directly from the strategic customer.  This began to lead to a disconnect
between what the marketing and sales organizations believed to be the overall
direction of the product, and the actual direction it was taking based on the
needs of a single customer. It was clearly time for a regroup, and the
engineering team pushed back on the MRD.  They were in full production mode
using Agile and they needed more granular, prioritized user stories to fuel
their efforts.  The teams needed product marketing to be more collaborative in
the decomposition of the requirements. This was a totally foreign concept for
the product marketing team. They had approached the relationship with
engineering as a “black box” – high level requirements went in, and something
eventually came out (usually late, and sometimes off the mark on what they
expected).

@@

* Solution: Development and product marketing work together
* Solution: Product marketing can require a release to be completed in 90 days
[P31]
What we instituted was what we call an “Iron Triangle.” The concept is that at
some number of sprints out before a release, we would commit to delivering a
fixed set of features and functionality  at a certain date.  Of course, there
was always the opportunity for us to deliver more than what we committed to, 
but we absolutely had to deliver the set features by the set date.

@@

% TOP LAYER OF ORGANIZATION IS IN WATERFALL MODE
% --> Generic ``PMO''
% 
% * Problem: PMO is employing a waterfall paradigm
% [P3]
% the Amazon PMO may some day become interested in Scrum, but they are enmeshed in
% maintaining and thriving within a traditional waterfall paradigm. Another
% example is the existence of separate QA groups. Executive sponsorship would help
% to begin to break down these entrenched impediments.
% 
% 
% * Problem: There was a gap between marketing or product management and development --> Requirement elaboration as cause
% [P5]
% We were able to successfully bridge the gap between marketing or product
% management feature and the detailed requirements that are required for Agile.
% 
% 
% * Challenge: PMO with entrenched processes
% * Challenge: Process group at odds with Scrum teams
% [P6]
% Align with Project Management: In any large organization like Yahoo! there
% inevitably exist Project Management Offices with entrenched process control
% practices. We had conflicts arise in our international offices as they had
% continued to roll out the original PDP during the U.S. transition to Scrum. The
% teams attempting to use Scrum were often at odds with the process group and, as
% a result, the two groups were not communicating well. We tackled this challenge
% by building relationships and identifying the common goals that both groups were
% focused on achieving.
% 
% 
% * Challenge: PMO was a bottleneck inhibiting agility
% [P46]
% To make this journey a success, it was clear that the transformation had to
% start with our strong PMO. Here we had the hub of all things project related –
% coordination, reporting, process quality assurance, compliance, code performance
% quality assurance and the 100+ project managers themselves – in a central place.
% Nothing happened without the PMO’s intimate involvement. It was a bottleneck
% that just could not exist for the organization to be agile. First and foremost,
% all the project managers were returned to their positions in the development
% organization, reporting directly to development managers. There the project
% managers (PMs) became accountable for project success – no longer were they
% simply facilitators and enforcers of the process. While they had always been
% accountable for truth in reporting, now they were accountable for results –
% their bonus was on the line.
% 
% * Problem: Development started with agile --> Other departments needed to adapt to iterative delivery
% [P17]
% Changes inevitably impact the rest of the company as all departments adapt to
% this new pace of incremental value delivery. Product managers must re-think how
% they define releases and work with development.

%--

% [P17] Like many organizations, BMC’s decision to adopt Agile practices started
% in the development organization.

% * Development was content with using agile only internally
% * General problem: Scaling agile practices into use in different roles
% [P2]
% One of the challenges faced by this organisation is how to extend an agile way
% of thinking beyond the developers, and both the Agile Advocates and Project Z
% believed that agile should cover the entire process

% * General challenge: Agile practices work worse in non-development
% [P18]
% Agile practices worked well in development teams and some other teams. Not
% surprisingly, the more distant from development, the less successful the pilot.
% 
% “Why change? Agile practices will not suit us.” The further away from actual
% software development, the less understanding about what benefits Agile ways of
% working will bring. The idea that Agile works best if customer contact and
% customer contract are synergistic does not easily penetrate a large
% organization.

% * Development of new products moved to agile first 
% * Problem: Moving the product from early access to GA --> Value chain has traditional parts
% [P31]
% The biggest bricks in our Two-Year Wall were being laid outside the development
% organization. The basic principles of Agile and lean are to reduce waste and
% deliver working software to the customer as often as possible. However, the
% development organization does not do this alone. When you look at the end-to-end
% process, there are many other functions involved:  sales, marketing, legal,
% finance. What we didn’t understand when we first embarked upon the Agile journey
% is what a disruptive force our approach would be on the entire company. As I
% mentioned earlier, the first teams to transition to Agile were those working on
% a new set of products. These teams had been working very closely with a
% strategic customer, and in the months prior to the public release of these
% products the situation was ideal for the collaboration, iteration and pace of
% releases. The reality is, in the first 18 months of our transformation the
% original Agile teams were operating as an “Agile microcosm” insulated from the
% rest of our traditional, multi-phased business processes. Once it became time to
% move the product from “early access” to general availability – to move from
% factory to inventory – things started to come apart.  Friction arose as the
% Agile teams began bumping up against the other, traditional, parts of the value
% chain.
% 
% * Development adopted first --> No plans for how to further adopt the rest of the stakeholders
% [P38]
% When suddenly the site that is the product in many of these cases could change
% literally on a week to week basis, you can see some of the issues that had to be
% addressed. In the agile world people often think “we can figure out how to
% interface with the rest of the business once we’ve gotten the team up and
% running” and while there are certainly teams that learn to interface with a
% non-agile business it is a risk and a barrier to change. In our case we were
% lucky that with the support of the CTO we were able to influence many elements
% of the business to be more agile themselves, which allowed them to work more
% effectively with the new agile development group.

% * Challenge: The entire organization must work in the same mode
% [P42]

@@

REQUIREMENT AND MRD COMMUNICATION PROBLEMS

* Not agile: MRDs --> Stories had to be extracted from detailed documentation --> Not good
* MRDs not based on reality
[P2]
Extracting user stories from existing, very detailed ‘marketing requirements
documents’ (MRDs) was another workaround. These MRDs were a prominent artifact
found across the organisation. Leaders of Project Z claimed that it was very
difficult to work with such detailed documents in a project whose scope could
change rapidly; one agile developer described MRDs as “not based in reality at
all”.
Comment:
The problem with MRDs is a symptom of the challenge to integrate "the business" with the agile process.

* Problem: Teams completed backlog --> Continued with stories direct from customer --> Single customer bias
* Problem: Sales and marketing organization had a different vision of the product
* Problem: Product marketing was not collaborative, and in old mindset
* Problem: Requirements --> user stories more granular and prioritized
[P31]

* Requirements engineering must be done differently
[P45]
Product teams had to communicate with business management, marketing, and field
services who were not fully prepared for how Scrum and the product teams’
expectations would change their daily work. The process of software requirements
engineering were found to require a major adjustment.
